Headgroup Structure and Cation Binding in Phosphatidylserine Lipid Bilayers

### 2019-08-21 Manuscript/manuscriptPS.tex
Updates based on editorial comments

\title{Headgroup structure and cation binding in phosphatidylserine lipid bilayers}

@@

\subsection{Molecular dynamics simulations}
Molecular dynamics simulation data were collected using
the Open Collaboration method \cite{botan15}, with
the NMR\-lipids Project blog (\url{nmrlipids.blogspot.fi}) and
GitHub repository (\url{github.com/NMRlipids/NMRlipidsIVotherHGs})
as the communication platforms.
The simulated systems are listed in 
Tables \ref{PSsystems} (pure PS bilayers without additional ions) 
and \ref{mixedIONsystems} (mixed PC:PS bilayers at various salt concentrations).
Further simulation details are given in the SI, and
the simulation data are indexed in a
searchable database available at \url{www.nmrlipids.fi},
and in the NMRlipids/MATCH repository (\url{github.com/NMRlipids/MATCH}).

@@

@@

% Create the reference section using BibTe
\bibliography{refs.bib}

>>>>

\title{Headgroup Structure and Cation Binding in Phosphatidylserine Lipid Bilayers}

@@

\subsection{Molecular dynamics simulations}
Molecular dynamics simulation data were collected using
the Open Collaboration method \cite{botan15}, with
the NMR\-lipids Project blog (\url{nmrlipids.blogspot.fi}) and
GitHub repository (\url{github.com/NMRlipids/NMRlipidsIVotherHGs})
as the communication platforms.
The simulated systems are listed in 
Tables \ref{PSsystems} (pure PS bilayers without additional ions) 
and \ref{mixedIONsystems} (mixed PC:PS bilayers at various salt concentrations).
Further simulation details are given in the SI, and
the simulation data are indexed in a
searchable database available at \url{www.nmrlipids.fi},
and in the NMRlipids/MATCH repository (\url{github.com/NMRlipids/MATCH})~\cite{MATCHgit}.

@@

\begin{suppinfo}

%A listing of the contents of each file supplied as Supporting Information 
%should be included. For instructions on what should be included in the 
%Supporting Information as well as how to prepare this material for 
%publications, refer to the journal's Instructions for Authors.

The following files are available free of charge. 
\begin{itemize} 
  \item SI.pdf: Additional simulation, experimental and methodological details, and further analysis. 
\end{itemize}

\end{suppinfo}

@@

% Create the reference section using BibTe
\bibliography{refsU.bib}
